How to compute the fusion product of MV cycles in type A

### 2021-04-14 draft.tex
mtg edits possibly compounded with other earlier edits

\section{Climax}
Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.  Note that $g(A)t^{-\mu} \in G_1(\Oinf)$.
% section ??.  
Since $ g(A) \in M_n(\CC[t]) \cap G_1(\Oinf)t^\mu$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.  (Alternatively, we can see that $ g(A) \CC[t]^m$ satisfies the condition (ii) from Lemma \ref{le:Wmu}.)

@@

On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is upper triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$.

\acom{$g(A)$ is lower-triangular}

@@

\subsection{Tableaux and families}
% 
TODO: resume here

$Z'\ast_\AA Z''$ is described by $\tau'\ast\tau''$

\begin{question}
    How do we know that our algorithm produces MV cycles? 
\end{question}

\begin{proposition}
    Let $\tau_1,\tau_2$\dots 
    \[
    \{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\mu^1 + \cdots + \mu^i} \in \OO_{0,s}^{\lambda_{1}^{(i)},\lambda_2^{(i)}} \text{ all } i\} = Z_{\tau_1}\times Z_{\tau_2}
    \]
\end{proposition}

\begin{proof}
    Want $L(0) \in Z(\tau_1)$ and $L(s) = Z(\tau_2)$. \acom{Another notational possibility is $\mu = \mu^0 + \mu^s$ etc., or $\mu(0) + \mu(s)$ or some variant with the eigenvalues being the indices.}

    Fix $i \in \{1,\dots,m\}$ and let $p = \mu^1 + \cdots + \mu^i$. 
    % Define $\lambda^{(i)}(\tau_1 \circ \tau_2)$ so that the 
    Jordan type of $t\big|_{\CC[t]^p/L(0)\cap\CC[t]^p}$ is $\lambda_1^{(i)}$ and Jordan type of $t-s\big|_{\CC[t]^p/L(s)\cap \CC[t]^p}$ is $\lambda_2^{(i)}$.

>>>>

\section{Climax}
Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.  Note that $g(A)t^{-\mu} \in G_1(\Oinf)$.
% section ??.  
Since $ g(A) \in M_m(\CC[t]) \cap G_1(\Oinf)t^\mu$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.  (Alternatively, we can see that $ g(A) \CC[t]^m$ satisfies the condition (ii) from Lemma \ref{le:Wmu}.)

@@

On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is lower-triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$.

@@

\subsection{Tableaux and families}
% 
Recall that there is an order on repeated entries of a semistandard Young tableau. 
% 
In this section we explain how to determine the ideal of $Z'\ast_\AA Z''$ from the minimal pair $(\tau',\tau'')$ corresponding to $(n_\bullet(Z'),n_\bullet(Z''))$.
% 
In particular, we prove that ``the generalized Spaltenstein map'' produces MV cycles.

Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as above, and recall the $\mu$-numeration of the standard basis of $\CC^N$. Given $A \in M_N(\CC)$ we'll denote by $A\big|_{\CC^i}$ the restriction of $A$ to the subspace spanned by the first $i$ standard basis vectors. Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ the shape of $\tau'(i),\tau''(i)$ resp.\ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all but its first $i$ boxes.

\acom{May want a more compact notation such as $A_{k}$}

\begin{proposition}
    Given $Z',Z''$, let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ be such that\dots If $s\ne 0$, then 
    \[
    \overline{\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{\mu_1 + \cdots + \mu_i}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,m\}} 
    \cong Z'\times Z'' \,. 
    % = Z(\tau')\times Z(\tau'')\,. 
    \]
\end{proposition}

\begin{proof}
    % \acom{Another notational possibility is $\mu = \mu^0 + \mu^s$ etc., or $\mu(0) + \mu(s)$ or some variant with the eigenvalues being the indices.}
    % 
    First, reformulate as 
    \[
    \begin{tikzcd}
        & (L,s) \in \Grbd \ar[dr,mapsto]\ar[dl,mapsto]\\
        t\big|_{\CC[t]^m/L} \in A & & (L(0),L(s)) \in B 
    \end{tikzcd}
    \]
    Fix $i \in \{1,\dots,m\}$, let $p = \mu_1 + \cdots + \mu_i$ and consider $(L',L'')\in Z'\times Z''$. 
    We need to show that the Jordan type of $t\big|_{\CC[t]^p/L(0)\cap\CC[t]^p}$ is $\lambda'{(p)}$ and Jordan type of $(t-s)\big|_{\CC[t]^p/L(s)\cap \CC[t]^p}$ is $\lambda''{(p)}$.
